Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-09 GWLDCII.tex
pictures and GNproof added to paper 2

%*****************
%%% WLD drawing and 2,6 shortcuts

@@

% vertices, radius
\newcommand{\drawWLD}[2]{

@@

\newcommand{\drawpolypart}[2]{
\pgfmathsetmacro{\n}{#1}
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\angle}{360/\n}
    \foreach \i in {1,2,...,\n} {
      \draw (\angle*\i+ \angle/2:\radius) node {$\bullet$};
     \pgfmathsetmacro{\x}{\angle*\i - \angle/2}
      \pgfmathsetmacro{\concave}{((\n-1.5)/\n)}
      \draw (\x:\radius cm) .. controls (\angle *\i: \concave* \radius cm) .. (\x + \angle:\radius cm);
      %\draw (\angle *\i: .8* \radius cm) node {$\bullet$};
    }

@@

% r, bumpr, s, bumps: r, s are start/end vertices, bumpr and bumps are how many steps to bump the start/end for multiple props on one edge
\newcommand{\drawprop}[4]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\bumps}{#4}
\pgfmathsetmacro{\perturbe}{\angle/\n}

\begin{scope}
%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[smallpropagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
\end{scope}
}

\newcommand{\drawlabeledprop}[5]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\bumps}{#4}
\pgfmathsetmacro{\perturbe}{\angle/\n}

@@

\newcommand{\drawchord}[2]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\s}{#2}

@@

\newcommand{\boundaryprop}[4]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\perturbe}{\angle/\n}

\begin{scope}
\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s - \angle:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[#4] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s:\radius);
\end{scope}

@@

\newcommand{\boundA}[3]{
	\pgfmathsetmacro{\r}{#1}
	\pgfmathsetmacro{\bumpr}{#2}
	\pgfmathsetmacro{\destination}{#3}
	\pgfmathsetmacro{\perturbe}{\angle/\n}
	\path [name path=polyedge1] (\angle*\r:\radius) -- (\angle*\r + \angle:\radius);
	\path [name path=radius1] (0:0) -- (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius);
	\draw[->,
	name intersections={of=polyedge1 and radius1,by=p},
	shorten >=\radius*0.1 cm] (p) ++(\angle*\r + \angle/2 + \bumpr*\perturbe:\radius*0.15) -- (\angle*\destination: \radius*1.15);

\newcommand{\boundB}[3]{
	\pgfmathsetmacro{\rangle}{#1*\angle + \angle/2 + #2*\angle/\n}
	\pgfmathsetmacro{\sangle}{#1*\angle + \angle/2 + #3*\angle/\n}

	\draw[->,shorten <=\radius*0.02cm,shorten >=\radius*0.05cm] (\rangle:\radius*1.05) -- (\sangle:\radius*1.05);

\newcommand{\makediag}[8]{
	\begin{tikzpicture}[rotate=60,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{6}{0.8}
	%\drawnumbers
	\drawprop{#1}{#2}{#3}{#4}
	\drawprop{#5}{#6}{#7}{#8}
	\end{scope}
	\end{tikzpicture}
}

@@

%\drawWLDfragment[number of nodes]{radius}{fraction of circle to be displayed}
\newcommand{\drawWLDfragment}[3][10]{
\pgfmathsetmacro{\n}{#1} % use this to get consistent spacing between nodes
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\fragment}{#3} % between 0 and 1, gets you that percentage of a circle
\pgfmathsetmacro{\halfangle}{360*\fragment/2}
\pgfmathsetmacro{\startpoint}{270 - \halfangle}
\pgfmathsetmacro{\endpoint}{270 + \halfangle}
\pgfmathsetmacro{\step}{2*\halfangle/\n} 
\pgfmathsetmacro{\zero}{\startpoint-0.5*\step} % so node i is at angle \zero + i*\step
\centerarc[black](0,0)(\startpoint:\endpoint:\radius)
}

\newcommand{\drawnumberspartial}{
\node (0,0) {$\bullet$};
  \foreach \i in {1,2,...,\n} {
  \pgfmathsetmacro{\x}{\step*\i}
  \draw (\zero + \x:\radius*1.15) node {\footnotesize \i};
}
}

\newcommand{\newnode}[3][left]{
	\node[label={[label distance=-1mm]#1:{\scriptsize $#3$}}] at (\zero + #2*\step:\radius) {\scriptsize $\bullet$};
	%\node[#1] at (\zero + #2*\step:\radius) {\scriptsize $#3$};
}

% messier but more flexible: use when you want more control over label placement
\newcommand{\newbetternode}[3][{label distance=-1mm]left}]{
	\node[label={#1:{\scriptsize $#3$}}] at (\zero + #2*\step:\radius) {\scriptsize $\bullet$};
	%\node[#1] at (\zero + #2*\step:\radius) {\scriptsize $#3$};
}

% \newprop[label position]{start node}{end node}{label}
\newcommand{\newprop}[4][midway,below]{
\pgfmathsetmacro{\startnode}{#2}
\pgfmathsetmacro{\endnode}{#3}

@@

\newcommand{\newpropbend}[3]{
\draw[smallpropagator] (\zero+#1*\step:\radius*1.1) to[bend left = #3] (\zero + #2*\step:\radius*1.1);
}

@@

We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and either:
\begin{itemize}
\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
  %a configuration \eqref{eq:2 prop config} in $D$
{\em or} 
\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}
We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$. By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

@@

From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.  Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$. This completes the base case.

\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{15}{2}
	%\drawnumbers
	%\drawprop{1}{0}{4}{0}
	\begin{scope}
	\clip (0,0) circle (\radius cm);
	\draw[propagator] (\angle*5.3:\radius*1.2cm) to [bend left=50] (\angle*7.7:\radius*1.2cm);
	\node at (\angle*6.5:\radius*0.6cm) {\footnotesize $p_1$};
	\end{scope}
    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$};
    \node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
     \node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
     \node at (10:\radius*0.5) {\small $\cP_{in}(q_1)$};
	\node[rotate = 45] at (\angle * 5.2:\radius) {\Large $($};
\node[rotate = -15] at (\angle * 2.7:\radius) {\Large $)$};
\node[rotate = 20] at (\angle* 4:\radius*1.2) {\em \scriptsize 1, 2 or 3 vertices};
		\end{scope}
	\end{tikzpicture}\eas

 %\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
 %    \node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
   %  \node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};

\sanote{played with Sian's code. May need to tweak this picture}
Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside. For the rest of this proof, we assume this orientation and drop the $<_{i_r}$ from the notation.

@@

@@

\begin{figure}
\includegraphics[scale=0.2]{locally_identical.jpg}
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
\end{figure}
\end{rmk}

@@

\begin{figure}
\includegraphics[width=15cm]{4th_vertex}
\caption{The two types of configuration in which a propagator could (in theory) contribute its $<_i$-maximal support vertex to $I_i$.}
\label{fig:no fourth vertex}
\end{figure}f

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.  Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}
\note{Right at the end when we put the tikz figures in, someone needs to go through this proof and replace ``leftmost two cases'' with ``Case 1 and 2'' etc, because the tikz picture is arranged differently}

@@

\begin{figure}
    \includegraphics[scale=0.8]{3cases}
    \caption{Four cases for admissible WLDs with no non-supporting vertices. The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
  \end{figure}

@@

\begin{figure}
\includegraphics[width=10cm]{V_diagram}
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
\label{fig V diagram}
\end{figure}

@@

\medskip  \sanote{Suggested breakpoint of theorem}

We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.  Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

>>>>

%*****************
%%% WLD drawing

@@

% to draw a (full) WLD; \drawWLD{8}{2} is a circle of radius 2 with 8 marked points
\newcommand{\drawWLD}[2]{

@@

% as above, but draws the outer edge of the polygon partition instead
\newcommand{\drawpolypart}[2]{
\pgfmathsetmacro{\n}{#1}
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\angle}{360/\n}
    \foreach \i in {1,2,...,\n} {
      \draw (\angle*\i+ \angle/2:\radius) node {$\bullet$};
     \pgfmathsetmacro{\x}{\angle*\i - \angle/2}
      \pgfmathsetmacro{\concave}{((\n-1.5)/\n)}
      \draw (\x:\radius cm) .. controls (\angle *\i: \concave* \radius cm) .. (\x + \angle:\radius cm);
      %\draw (\angle *\i: .8* \radius cm) node {$\bullet$};
    }

@@

% to draw a propagator in a WLD: \drawprop{a}{b}{c}{d} draws a prop from edge a (offset by b from the centre of the edge)
% to edge c (offset by d from the centre)
\newcommand{\drawprop}[4]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\bumps}{#4}
\pgfmathsetmacro{\perturbe}{\angle/\n}
\begin{scope}
%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[smallpropagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
\end{scope}
}

% as above but the 5th argument labels the prop (must include formatting, $ signs, etc)
\newcommand{\drawlabeledprop}[5]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\bumps}{#4}
\pgfmathsetmacro{\perturbe}{\angle/\n}

@@

% \drawchord{a}{b} draws a straight line from vertex a to vertex b in the polygon partition
\newcommand{\drawchord}[2]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\s}{#2}

@@

@@

@@

%\drawWLDfragment[number of nodes, default = 10]{radius}{fraction of circle to be displayed}
% unlike \drawWLD above, nodes are not marked by default, use \newnode below 
\newcommand{\drawWLDfragment}[3][10]{
\pgfmathsetmacro{\n}{#1} % use this to get consistent spacing between nodes
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\fragment}{#3} % between 0 and 1, gets you that percentage of a circle
\pgfmathsetmacro{\halfangle}{360*\fragment/2}
\pgfmathsetmacro{\startpoint}{270 - \halfangle}
\pgfmathsetmacro{\endpoint}{270 + \halfangle}
\pgfmathsetmacro{\step}{2*\halfangle/\n} 
\pgfmathsetmacro{\zero}{\startpoint-0.5*\step} % so node i is at angle \zero + i*\step
\centerarc[black](0,0)(\startpoint:\endpoint:\radius)
}

% puts numbers on the partialWLD; only really useful for debugging
\newcommand{\drawnumberspartial}{
\node (0,0) {$\bullet$};
  \foreach \i in {1,2,...,\n} {
  \pgfmathsetmacro{\x}{\step*\i}
  \draw (\zero + \x:\radius*1.15) node {\footnotesize \i};
}
}

% \newnode[location]{b}{c} puts a dot on the node at position b, with label c. location = left by default
\newcommand{\newnode}[3][left]{
	\node[label={[label distance=-1mm]#1:{\scriptsize $#3$}}] at (\zero + #2*\step:\radius) {\scriptsize $\bullet$};
	%\node[#1] at (\zero + #2*\step:\radius) {\scriptsize $#3$};
}

% messier but more flexible: use when you want more control over label placement

\newcommand{\newbetternode}[3][{label distance=-1mm]left}]{
	\node[label={#1:{\scriptsize $#3$}}] at (\zero + #2*\step:\radius) {\scriptsize $\bullet$};
	%\node[#1] at (\zero + #2*\step:\radius) {\scriptsize $#3$};
}

% \newprop[label position]{start node}{end node}{label}; for \partialWLD only
\newcommand{\newprop}[4][midway,below]{
\pgfmathsetmacro{\startnode}{#2}
\pgfmathsetmacro{\endnode}{#3}

@@

% as above but with a bend in it; \newpropbend{startnode}{endnode}{bend in degrees}
% note that the propagator extends past the edge of the diagram: always use this in a scope with \clipcenterarc (above)
\newcommand{\newpropbend}[3]{
\draw[smallpropagator] (\zero+#1*\step:\radius*1.1) to[bend left = #3] (\zero + #2*\step:\radius*1.1);
}

@@

We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and either:
\begin{itemize}
\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
  %a configuration \eqref{eq:2 prop config} in $D$
{\em or} 
\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
	\begin{scope}
	\drawWLDfragment[10]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\centerarc[linehighlight](0,0)(\zero + 1.5*\step:\zero + 2.35*\step:\radius)
	\newnode{1}{}
	\newnode{3}{}
	\newnode{4}{}
	\newnode{5}{}
	\newnode[below]{9}{i_1}
	\newnode{10}{}
	\newprop[midway,above]{1.4}{9.5}{\footnotesize $q_1$}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\newpropbend{2.3}{4.7}{60}
		\node at (\zero + 3.5*\step:\radius*0.78) {\footnotesize $p_1$};
	\end{scope}
\node[align = center] at (\zero +1.7*\step:\radius*1.4) {\footnotesize \em 0, 1, or 2 \\ \footnotesize \em vertices in \\ \footnotesize \em this region};
\node at (\zero + 10*\step:\radius*0.3) {$\cP_{in}(q_1)$};
\end{scope}
\end{tikzpicture}
\]
\caption{The base case of the induction in Lemma~\ref{lem sian}.}\label{fig base case lem sian} \end{figure}

We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$. By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

@@

From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.  Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}. This completes the base case.

Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside. For the rest of this proof, we assume this orientation and drop the $<_{i_r}$ from the notation.

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[15]{4}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i_r}
	\newnode[left]{2}{i_r+1}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode[right]{14}{k_r}
	\newnode[right]{15}{k_r+1}
	\newprop[midway,above]{1.5}{14.5}{\footnotesize $q_r$}
	\draw[smallpropagator,gray] (\zero+2.5*\step:\radius) -- (\zero + 12.5*\step:\radius) node[midway,above,gray] {\footnotesize $q_{r}'$};
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\newpropbend{5.2}{7.7}{80}
		\node at (\zero + 6.5*\step:\radius*0.85) {\footnotesize $p_{r+1}$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{We can replace $q_r$ with $q'_r$ as long as the conditions of the induction hypothesis remain satisfied.}
\label{fig smallest q in lem sian}
\end{figure}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{-4}{}
		\node at (\zero + 3*\step:\radius*0.5) {\footnotesize $p$};
		\newprop[midway]{11.5}{-4}{}
		\node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{2}{m}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{19}{}
		\node at (\zero + 5.5*\step:\radius*0.5) {\footnotesize $s$};
		\newprop[midway]{11.5}{21}{}
		\node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
\end{figure}
\end{rmk}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[20]{2}{1}
	%\drawnumbers % use this to debug
	\newnode[left]{4}{I_i(p) = i-1}
	\newnode[left]{5}{i}
	\newnode[left]{7}{c}
	\newnode[left]{8}{}
	\newnode[right]{15}{b}
	\newnode[right]{16}{b+1}
	\newprop[midway,above]{4.7}{15.7}{\scriptsize $p$}
	\newprop[midway,below]{7.5}{15.3}{\scriptsize $q$}
      \draw[smallpropagator,light-gray] (\zero +\step *4.3:\radius*1) -- (90:\radius*0.5); 
	\node at (270:\radius*1.5) {\em Case 1};
	% \begin{scope}
	% \clip (\zero + 5*\step:\radius*1.1) rectangle (90:\radius*0.8);
	% \draw[smallpropagator,color=gray] (\zero+4.5*\step:\radius) -- (\zero + 19*\step:\radius);
	% \end{scope}
		\end{scope}
	\end{tikzpicture}
\qquad \qquad 
	\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[20]{2}{1}
	%\drawnumbers % use this to debug
	\newnode[left]{4}{a}
	\newnode[left]{5}{}
	\newnode[left]{7}{}
	\newnode[left]{8}{}
	\newnode[right]{15}{b}
	\newnode[right]{16}{b+1 = I_i(p)}
	\newnode[below]{11}{d}
	\newnode[below]{12}{}
	\newnode[above]{2}{i}
	\newprop[midway,above]{4.5}{15.7}{\scriptsize $p$}
		\node at (270:\radius*1.5) {\em Case 2};
	\begin{scope}
	\clip (0,0) circle (\radius);
	%q
	\draw[smallpropagator] (\zero+11.5*\step:\radius*1.2) to [bend left = 45] (\zero + 15.5*\step:\radius*1.2); 
	\node at (\zero + 13.5*\step:\radius*0.55) {\scriptsize $q$};
	%r
	\draw[smallpropagator] (\zero+7.5*\step:\radius*1.2) to [bend left = 45] (\zero + 11.4*\step:\radius*1.2);
	\node at (\zero + 9.5*\step:\radius*0.55) {\scriptsize $r$};

	\end{scope}
		\end{scope}
	\end{tikzpicture}
\] 
\caption{The two types of configuration in which a propagator could (in theory) contribute its $<_i$-maximal support vertex to $I_i$.}
\label{fig:no fourth vertex}
\end{figure}f

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.  Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}
\note{This proof needs to be updated to refer to the new figure (e.g. case 1 and 2 instead of ``leftmost two cases''); also check that all the vertices are labeled correctly}

@@

\begin{figure}
\begin{tabular}{lll}
% case 1
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[8]{3}{0.3} % draws the arc and sets up the parameters
	%\drawnumbers % use this to debug
	% next two lines draw the highlighted regions
	\centerarc[linehighlight](0,0)(\zero + 1.85*\step:\zero + 4.4*\step:\radius)
	\centerarc[linehighlight](0,0)(\zero + 6.75*\step:\zero + 7.4*\step:\radius)
	% labels explaining the highlighted regions
	\node[align = center] at (\zero + 2.7*\step:\radius*1.3) {\em \footnotesize 1 or 2 vertices \\[3pt] \em \footnotesize in this region};
	\node[align = center] at (\zero + 7.5*\step:\radius*1.4) {\em \footnotesize 0 or 1 vertices \\[3pt]\em \footnotesize in this region};
	\begin{scope} % this scope draws the propagators and their labels
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%q
		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
		%p
		\draw[smallpropagator] (\zero+4.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.8*\step:\radius*1.1); 
		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
		\node at (\zero + 5.5*\step:\radius*0.8){\footnotesize $p$};
	\end{scope}
	% draw the nodes
	\newnode[left]{1}{i}
	\newnode[right]{8}{j+1}
	\newnode[below]{5}{}
	\newnode[below]{6}{}
% case label
\node at (270:\radius*0.2) {\em Case 1};
\end{scope}
\end{tikzpicture}
%
%
%
& \qquad \qquad &
%
%
%
% case 2
\begin{tikzpicture}[baseline=(current bounding box.east)]
\begin{scope}
	\drawWLDfragment[8]{3}{0.3} % draw arc
	%\drawnumbers % use this to debug
	% highlighted regions
	\centerarc[linehighlight](0,0)(\zero + 1.85*\step:\zero + 2.4*\step:\radius)
	\centerarc[linehighlight](0,0)(\zero + 4.75*\step:\zero + 7.4*\step:\radius)
	%labels for highlighted regions
	\node[align = center] at (\zero + 6.6*\step:\radius*1.3) {\em \footnotesize 1 or 2 vertices \\[3pt]\em \footnotesize in this region};
	\node[align = center] at (\zero + 1.6*\step:\radius*1.35) {\em \footnotesize 0 or 1 vertices \\[3pt]\em \footnotesize in this region};
	% draw props and their labels
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%q
		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
		%p
		\draw[smallpropagator] (\zero+2.3*\step:\radius*1.1) to [bend left = 55] (\zero + 4.8*\step:\radius*1.1); 
		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
		\node at (\zero + 3.5*\step:\radius*0.8){\footnotesize $p$};
	\end{scope}
	% nodes
	\newnode[left]{1}{i}
	\newnode[right]{8}{j+1}
	\newnode[below]{3}{}
	\newnode[below]{4}{}
	% case label
	\node at (270:\radius*0.2) {\em Case 2};
\end{scope}
\end{tikzpicture}
%
%
%
\\
\ & \ & \ \\
%
%
%
% case 3
\begin{tikzpicture}[baseline=(current bounding box.east)]
\begin{scope}
	\drawWLDfragment[8]{3}{0.3} % draw arc
	%\drawnumbers % use this to debug
	% highlight region
	\centerarc[linehighlight](0,0)(\zero + 3.6*\step:\zero + 5.4*\step:\radius)
	% region label
	\node[align = center] at (\zero + 4.5*\step:\radius*1.3) {\em \footnotesize 0, 1, or 2 vertices \\[3pt]\em \footnotesize in this region};
	% scope to draw props and their labels
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%q
		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to [bend left = 55] (\zero + 3.7*\step:\radius*1.1); 
		%p
		\draw[smallpropagator] (\zero+5.3*\step:\radius*1.1) to [bend left = 55] (\zero + 7.6*\step:\radius*1.1); 
		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
		\node at (\zero + 2.8*\step:\radius*0.8){\footnotesize $q$};
		\node at (\zero + 6.5*\step:\radius*0.8){\footnotesize $p$};
	\end{scope}
	% draw nodes
	\newnode[left]{1}{i}
	\newnode[below]{2}{}
	\newnode[below]{3}{j}
	\newnode[below]{6}{}
	\newnode[below]{7}{}
	\newnode[right]{8}{}
	% case label
	\node at (270:\radius*0.2) {\em Case 3};
\end{scope}
\end{tikzpicture}
%
%
%
& \qquad \qquad & \qquad
%
%
%
% case 4
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[8]{3}{0.3} % draw arc
	%\drawnumbers % use this to debug
	%scope to draw props and their labels
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%q
		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
		%p
		\draw[smallpropagator] (\zero+3.3*\step:\radius*1.1) to [bend left = 55] (\zero + 5.8*\step:\radius*1.1); 
		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
		\node at (\zero + 5*\step:\radius*0.8){\footnotesize $p$};
	\end{scope}
	% draw nodes
	\newnode[left]{1}{i}
	\newnode[below]{2}{i+1\quad }
	\newnode[below]{3}{l\quad}
	\newnode[below]{4}{l+1\ \ }
	\newnode[below]{5}{\ \ l+2}
	\newnode[below]{6}{\quad l+3}
	\newnode[below]{7}{\quad j}
	\newnode[right]{8}{j+1}
	% case label
	\node at (270:\radius*0.2) {\em Case 4};
\end{scope}
\end{tikzpicture}
\end{tabular}
    \caption{Four cases for admissible WLDs with no non-supporting vertices. The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
  \end{figure}

@@

@@
